Project Proposal

### 2024-11-17 NFL_IDS702Projectproposal.qmd
update nfl Q1

ggpairs(
  nfldata_1_viz,
  columns = c("dropbackCategory", "dropbackDistance" ),
  aes(color = as.factor(passResult)), # Treat passResult as a factor
  upper = list(continuous = "points"),
  lower = list(continuous = "points")
) +
  labs(
    title = "Pairwise Plots of Predictors Colored by Pass Result",
    color = "Pass Result"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5, face = "bold"),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )

>>>>

ggpairs(
  nfldata_1_viz,
  columns = c("dropbackCategory", "dropbackDistance","timeToThrow", "passLength" ),
  aes(color = as.factor(passResult)), # Treat passResult as a factor
  upper = list(continuous = "points"),
  lower = list(continuous = "points")
) +
  labs(
    title = "Pairwise Plots of Predictors Colored by Pass Result",
    x = "Predictor 1",
    y = "Predictor 2",
    color = "Pass Result"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5, face = "bold"),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )
